---
title: "Initialize ECOS archive"
author: "Jacob Malcom, Defenders of Wildlife"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: yeti
---

```{r setup, include=FALSE}
library(dplyr)
library(ecosdata)
library(ecosscraper)
library(knitr)
```

# Get Base dfs

## TECP_table

Before initializing the run across all T & E species, we need to get up-to-date
data from the main table of ECOS:

```{r TECP}
TECP_init <- get_TECP_baseline()
TECP_table <- TECP_init$TECP_table
TECP_summary <- TECP_init$TECP_summary
kable(head(TECP_table))
```

At this initial scrape, it is interesting to see one Hawaiian species' common
name, which features backticks, gets turned to "code" (_Abutilon menziesii_). 
We will keep the summary df of the TECP_table for joining with the per-species 
page scrape summary data, to be saved later.

## Filter species

By default, `get_TECP_table` records foreign + domestic and T & E + candidates /
proposed. But we're primarily interested in domestic T & E only, so we filter:

```{r domestic}
dom <- filter_listed(TECP_table) %>% filter_domestic()
kable(head(dom))
```

# Species' Pages

Now we can get baseline data on every species' ECOS page.

```{r scrape_species}
sp_base <- get_species_baseline(dom$Species_Page[1:3], 
                                dom$Scientific_Name[1:3], 
                                FALSE)
sp_summary <- bind_rows(sp_base)
kable(head(sp_summary))
```

# Save .rdas

Last, for now, we will combine the data and save it as `.rda`:

```{r save_data}
TECP_summary$Type <- "TECP_table"
sp_summary$Type <- rep("species_page", length(sp_summary$Species))
ECOS_summary <- rbind(TECP_summary, sp_summary)
kable(head(ECOS_summary))
save(ECOS_summary, file = "../data/ECOS_summary.rda")
```
